\bf An HMM-based part-of-speech tagger for Turkish

### 2015-11-17 proposal/proposal.tex
Fix things

For programming the POS tagger I will be using Haskell, a statically-typed and purely
functional programming language, along with the
\href{\hmmURL}{\texttt{Data.HMM}} package.
The data, that is probably the most important component of this
project, comes from the METU-Sabanc\i treebank built by
\citet{oflazer2003building}.  I will be stripping the POS tag for each word from
the corpus and will use them to train HMM's.

>>>>

For programming the POS tagger I will be using Haskell, a statically-typed and purely
functional programming language, along with the
\href{\hmmURL}{\texttt{Data.HMM}} package.
The data, that is probably the most important component of this
project, comes from the METU-Sabanc{\i} treebank built by
\citet{oflazer2003building}.  I am planning to strip the POS tag for each word from
the treebank and use those to train the HMM
